Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-22 docs/manuscript/manuscript.tex
Updates from Overleaf

\subsection{Model visualization and inference}

@@

\section{Data Availability Statement}
All data, models, or code generated or used during the study are available in a repository online in accordance with funder data retention policies (provide full citations that include URLS or DOIs)

>>>>

\subsection{Analysis of classification strategies}
We investigated in the detail the performance of the four classification scenarios earlier outlined, using the 64px resolution images.
The goal of this analysis was to explore the efficiencies of various grouping strategies for tree failure risk.
In addition to overall accuracy of making correct classifications, we assessed the models trained under these scenarios based on the weighted averages of the precision, recall and $F_1$ score metrics.

\begin{align}
\text{Weighted average precision: }    Pr^w &= \frac{1}{\sum_{c\in C} n_c} \sum_{c\in C} \left(  \frac{n_c TP_{c} }{TP_{c} + FP_c}\right) \\
\text{Weighted average recall: }    Re^w &= \frac{1}{\sum_{c\in C} n_c} \sum_{c\in C} \left(  \frac{n_c TP_{c} }{TP_{c} + FN_c}\right) \\
\text{Weighted average $F_1$ score: }    F_1^w &= \frac{1}{\sum_{c\in C} n_c} \sum_{c\in C} \left(  \frac{2 n_c Pr_{c} Re_{c}}{Pr_c + Re_c}\right)
\end{align}
where the class-based metrics are given by:
\begin{align}
    TP_c &= \sum_{i \in c} I(\hat{y}_i = y_i ) \\
    FP_c &= \sum_{i \in c} I(\hat{y}_i \in c | y_i \notin c) \\
    FN_c &= \sum_{i \in c} I(\hat{y}_i \notin c | y_i \in c)
\end{align}
\subsection{Model visualization and inference}

@@

\section{Data Availability Statement}
All data, models, or code generated or used during the study are available in a GitHub repository online at \url{https://github.com/narslab/tree-risk-ai}.
